\documentclass{article}
\usepackage{titlesec}
\usepackage{array, xcolor}
\usepackage[margin=1.5cm]{geometry}

\title{\bfseries\Large Tony Gaetani}
\author{tony.gaetani@gmail.com -- https://tonygaetani.com}
\date{}

\definecolor{lightgray}{gray}{0.8}
\newcolumntype{L}{>{\raggedleft}p{0.2\textwidth}}
\newcolumntype{R}{p{0.65\textwidth}}

\begin{document}
\pagenumbering{gobble}
\maketitle

\section*{About}
Seeking employment in Chicago, IL in September 2016.\\\\
Software Engineer with 5 years of experience designing and developing software.\\\\
Strong skills in C++, Java, Python, Clojure, SQL databases and Linux server administration.\\\\
Proven ability to solve challenging problems by learning new technologies and working in teams.
%% \begin{itemize}
%%   \item Seeking employment in Chicago, IL in September 2016.
%%   \item Software Engineer with 5 years of experience designing and developing software.
%% %% Software Engineer with 6+ years of experience in desktop, mobile and web application development.\\
%%   \item Strong skills in C++, Java, Python, Clojure, SQL databases and Linux server administration.
%%   \item Proven ability to solve challenging problems by learning new technologies and working in teams.
%% %% Experienced in SQL databases, Linux server administration, security and configuration management.\\
%% %% Delivered successful products in teams and individually.\\
%% %% Proven ability to solve challenging problems, work in teams and deliver successful products.\\
%% \end{itemize}

\section*{Professional Experience}
{\large {\bf Back-end Software Engineer} Conceptboard, Stuttgart, Germany}\\
Nov 2014 -- Jun 2016
\begin{itemize}
  \item {\bf Java development}, mainly focusing on designing and implementing microservices.
  \item {\bf Development operations} on Linux and Mac.
  \item Used Puppet and Bash to develop Linux server configurations and automate deployment.
  %% \item Generated cash by developing a standalone version of existing SaaS product to be sold as an on-premises solution.
  \item Developed a standalone version of the Conceptboard SaaS product to be sold as an on-premises solution.\\
\end{itemize}
{\large {\bf Senior Software Engineer} Mimio, Cambridge, Massachusetts}\\
Nov 2010 -- Jun 2014
\begin{itemize}
  \item {\bf Cross-platform C++ development} of multilingual applications and libraries.
  \item Worked in teams of 2-5 developers on Linux, Mac, Windows, iOS and Android applications.
  \item Lead developer for USB device integrations, designed and implemented USB device protocols.
  \item Received multiple awards for individual contributions to the company and work environment.
\end{itemize}

\section*{Education}
{\large {\bf BSc in Software Engineering}, Champlain College, Vermont}\\
Sep 2006 -- May 2010
\end{document}
